Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-17 manuscripts/paper-1/main.tex
Last_Draft

    These days, there is evidence that digital twins play a crucial role in the manufacturing industries, 
    life sciences, healthcare, infrastructure and smart cities\cite{Review2}.
    For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
    and later is used to collect and analyze the data from the real system for making the process of the real system more efficient \cite{GeneralElectricWindTurbine}. 
    Another fascinating example of the use of digital twins is Philips' virtual heart model. Twin of the heart evolves with the  data generated by ultrasonic sensors to calculate 
    how well the real heart is pumping the blood. This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment \cite{PhilipsHearth}. 
    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments. To ensure the quality of these digital twins, a specific Verification \& Validation process is implemented ~\cite{FELICE}.

@@

    This paper aims to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with FELICE's digital twin system~\cite{FELICE}. 
    The evaluation aims to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
    a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module. 
    To evaluate these artifacts, we considered five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.

@@

    \subsection{Software quality}
    Software is a combination of programs and data that can be utilized by both virtual and physical systems, 
    such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set \cite{IEE730-2014}. 
    As an example, ISO/IEC:25010 has standardized eight attributes, 
    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality.

    \subsection{Simulation Quality}
    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system 
    \cite{MobusSystemTheory}. However, these days, many simulation processes are done by virtual systems. For example,  software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users 
    to build a simulation model to make predictions and get information about the past - as well as the current state - of the system.  
    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques \cite{StewartSimulation} \cite{VerificationValidationSergent} \cite{OsmanBalci}.

    Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications. 
    On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation}\cite{VerificationValidationSergent}. 
    These techniques are broadly categorized into six areas: informal, static, dynamic, 
    symbolic, constraint, and formal techniques \cite{balcicategories}\cite{balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used \cite{balcicategories}.

@@

    \textbf{Discrete Event Simulation Model} consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section. 
    The animation sections provided a two-dimensional and a three-dimensional representation of the system, 
    which aided in understanding the simulation and debugging purposes. The input sections allowed for the management of inputs to the simulation model, and the output section displayed summary performance indicators about the simulation run. 
    The process logic section contained the process building blocks, such as queues and assembly operations. Lastly, the database section provided an interface to data sources and sinks.

@@

    \textbf{Correctness} is a  derived word from the adjective \textit{correct}, which means that the entity is error-free regarding fact or truth. 
    In the context of the digital twins, the fact or truth is the real system hence, \textit{correctness} is a grade of quality, 
    that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}). This 
    Meanwhile, the quality of being \textit{correct} is described by the term accuracy \cite{OxfordDictionary}.

    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
    (Figure~\ref{fig:CorrectnessAndCompleteness}). Additionally, subaspects of completeness, which are \textit{incompleteness} and \textit{overcompleteness} 
    were inspected but identified as a completeness issue.

@@

        \centering
            \includegraphics[width = 1\textwidth]{Correctness and Completeness.png}
            \caption{Correctness and Completeness}\label{fig:CorrectnessAndCompleteness}
    \end{figure}

    \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. 
    Low fidelity indicates a simplified representation, 
    while high fidelity refers to an accurate and detailed representation of the real system~\cite{Review2} (Figure~\ref{fig:EfficiencyandFidelity}). 
    The concept of fidelity has garnered significant attention in recent
    years and continues to be an important focus in Digital Twin research\cite{Review2}\cite{Review1}.

    \textbf{Efficiency} refers to the quality of being efficient\cite{OxfordDictionary}. 
    Therefore, efficiency is achieving maximum productivity with minimum wasted effort or expense (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of efficiency is tightly intertwined with the concept of productivity, 
    although it differs from the latter's definition, which is defined as the ability to produce large amounts of goods\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired.

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
        \caption{Efficiency and Fidelity}~\label{fig:EfficiencyandFidelity}
    \end{figure}

    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is an evolvable virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}. 
    Furthermore, the evolvability of the digital twin was assessed based on the quantity of effort, which is a neccessaryy resource to initiate transformation
    within the system (Figure~\ref{fig:Evolvability}).

    \begin{figure}[htbp]
        \includegraphics[width = 1\textwidth]{Evolvability.png}
        \caption{Evolvability}
        ~\label{fig:Evolvability}
    \end{figure}

    \subsection{Mapping Digital Twin Attributes to Manual Review Results}
    To evaluate the quality of the artifact, the issues were mapped to digital twin attributes. 
    To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation.

    \subsection{Artifact Quality Evaluation}
    To evaluate the quality of the digital twin artifacts, the mapped findings were scrutinized and evaluated. 
    The process started by identifying which quality attribute(s) were mapped. 
    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality missing attributes of the artifact.

@@

    \subsection{Digital Twin Quality Evaluation}
    To assess the quality of the digital twin, the values obtained from evaluating each artifact's quality are collected and summed. 
    The resulting sum was assigned to the corresponding digital twin quality attribute. 
    As a result, the digital twin quality was expressed with quality attribute values.

@@

    %TODO REWRITE HERE FOR NOVELTY
    First, to assess digital twin quality,
    manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
    As a result, a total of twenty-one quality issues were identified,
    listed and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
    The mapping process 
    revealed that a total of thirty-eight digital twin quality attributes were 
    lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
    Specifically, 23\% of the quality issues of the digital twin were related to correctness, 
    which indicates an error between the real- and digital twin system. 36\%  were related to completeness, 
    proving that some necessary or appropriate parts were missing.
    8\%  were related to fidelity, indicating a lack of detail. 
    5\%  were related to efficiency, indicating poor performance or excessive resource usage.
    and finally, 28\% were related to evolvability, indicating that the system was unresponsive to the environment and was not flexible or scalable.

    \subsection{Example Findings}  
    Two examples(Finding 12, Finding 18) are given to the reader o illustrate 
    the results of the manual review as well as the mapping to the digital twin quality attributes.

    \subsubsection{Conceptual Model-Finding 12}

@@

    \subsubsection{Simulation Model-Finding 18 }
        The discrete event simulation model enforced a strictly sequential execution of micro-operations,
        which precludes the support of parallel execution. 
        However, machine-human collaboration on a task, needs a parallel execution, especially when the cobot overtakes certain micro-operations. 
        Thus, the exclusion of parallel executions indicates that the simulation model was incomplete,
        at the same time using the wrong type of execution highlights its inaccuracies(Table~\ref{tab:Table1}) .

@@

    \caption{Mapping of digital twin attributes to the results of the manual reviews: In cases where an attribute is mapped shown by `X'.}
    \label{tab:Table1}

@@

    The results of this study demonstrate that a manual review and mapping of quality attributes to issues is an effective approach for evaluating the quality of digital twins in the design phase.  
    Therefore, systematic analysis of the identified issues in terms of their relevance to various quality attributes is an effective way to gain insight into the strengths and weaknesses of the digital twin system under development. 
    These insights can be used to guide further design decisions and improvements, ultimately leading to a higher-quality end product.

    The quality assessment of the digital twin encountered limitations due to the exility of information about the real system. Some artifacts provided less information, 
    such as process videos, which only provide a limited perspective of the shop floor based on the camera's field of view and the skills of the video maker. 
    In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, which results in a higher probability of discovering the issues~\ref{fig:QualityInspectonResultsWithArtifacts}.

    Person dependent, also not everything is written, memory problem, completeness, 
    issuee finding sometimes even though the issue is not there, still assesed as a issue, assuming that person is correct

    The write a protocol, timing ,hard to cover everything,

>>>>

    In recent years, there is evidence that digital twins play a crucial role in the manufacturing industries, 
    life sciences, healthcare, infrastructure and smart cities\cite{Review2}.
    For example, a digital wind farm from General Electric is a good illustration of how building a digital twin helped to design a better turbine, 
    which was used to collect and analyze the data from the real system for making the process of the real system more efficient~\cite{GeneralElectricWindTurbine}. 
    Another fascinating example of the use of digital twins is Philips' virtual heart model. The twin of the heart evolves with the data generated by ultrasonic sensors to calculate 
    how well the real heart is pumping the blood. This information can be used to predict a potential heart failure, allowing for early intervention and potentially life-saving treatment~\cite{PhilipsHearth}. 
    Lastly, FELICE is another interesting example of a digital twin application in manufacturing. In the project, twin models of machines/equipment and 
    agents are utilized to support real-time decision-making and to conduct what-if analysis and experiments~\cite{FELICE}.

@@

    This paper aims not only to review the digital twin artifacts utilized in the FELICE project and evaluate the quality issues associated with them~\cite{FELICE}. 
    also, targets to enhance the scientific understanding of the quality of digital twins. The artifacts analyzed in this study include process videos showing the current assembly procedure, 
    a scope definition, a requirements specification, a general and operational conceptual model, and a discrete event simulation module. 
    To evaluate these artifacts, we considered five crucial quality attributes: correctness, completeness, fidelity, efficiency, and evolvability.

@@

    \subsection{Software quality}
    Software is a combination of programs and data that can be utilized by both virtual and physical systems, 
    such as computer systems\cite{OxfordDictionary}. Its quality is determined by how well it fulfills the requirements that were set. However, 
    those requirements may not always reflect the needs of the stakeholders, hence the quality depends on how accurately these requirements were set~\cite{IEE730-2014}. 
    As an example, ISO/IEC:25010 has standardized eight attributes, 
    including functional suitability, performance efficiency, compatibility, usability, reliability, security, maintainability, and portability, to measure software quality.

    \subsection{Simulation Quality}
    The human brain simulates real systems abstractly either to predict the future state of the system or to gather information about the past state of the system 
    \cite{MobusSystemTheory}. However, these days, many simulation processes are done by virtual systems. For example,  software programs such as ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic} enable users 
    to build a simulation model to make predictions and get information about the past- as well as the current state of the system.

    Quality characteristics of these simulation models must be evaluated by the validation and verification techniques~\cite{StewartSimulation,VerificationValidationSergent,OsmanBalci}. Validation is the process of evaluating the simulation quality in comparison to the real system from the perspective of its intended applications. 
    On the other hand, verification is a procedure to evaluate the implementation of the simulation model and 
    its associated data concerning the conceptual description and specifications of the model developer\cite{StewartSimulation,VerificationValidationSergent}. 
    These techniques are broadly categorized into six areas: informal, static, dynamic, 
    symbolic, constraint, and formal techniques \cite{balcicategories,balcitechniques}. Formal techniques involve mathematical formality, whereas informal techniques rely on 
    human intervention and reasoning. Although mathematical techniques are more precise, informal techniques are more commonly used \cite{balcicategories}.

@@

    %%TODO
    \textbf{Discrete Event Simulation Model} consisted of seven sections, including two animation sections, two input sections, one output section, one process logic section, and a database section. 
    The animation sections provided a two-dimensional and a three-dimensional representation of the system, 
    which aided in understanding the simulation and debugging purposes. The input sections allowed for the management of inputs to the simulation model, and the output section displayed summary performance indicators about the simulation run. 
    The process logic section contained the process building blocks, such as queues and assembly operations. Lastly, the database section provided an interface to data sources and sinks.

@@

    \textbf{Correctness} is a  derived word from the adjective \textit{correct}, which means that the entity is error-free regarding fact or truth. 
    In the context of the digital twins, the fact or truth is the real system hence, \textit{correctness} is a grade of quality, 
    that indicates an error between the real system and a digital twin system (Figure~\ref{fig:CorrectnessAndCompleteness}).
    Meanwhile, the quality of being \textit{correct} is described by the term accuracy~\cite{OxfordDictionary}.

    %%TODO
    \textbf{Completeness} is a derived word from the word  \textit{complete}, which can be described as an adjective, attribute, or verb\cite{OxfordDictionary}. 
    The adjectival form used in the study denotes \textit{complete} as a state of having all the necessary or appropriate parts according to the real system 
    (Figure~\ref{fig:CorrectnessAndCompleteness}). Additionally, subaspects of completeness, which are \textit{incompleteness} and \textit{overcompleteness} 
    were inspected but identified as a completeness issue.

@@

        \centering
            \includegraphics[width = 1\textwidth]{Correctness and Completeness.png}
            \caption{Incorrect  (a) and incomplete (b) status has been demonstrated with a 
            simplified finite state machine. Incorrectness can be observed in the behavior 
            of the machine after 2 state transitions. Incompleteness, on the other hand, can be observed in 
            the missing state. It should be noted that, even though the second state machine is missing a 
            component, it shows the right behavior, hence it is correct. }\label{fig:CorrectnessAndCompleteness}
    \end{figure}

    \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. 
    Low fidelity indicates a simplified representation, 
    while high fidelity refers to an accurate and detailed representation of the real system~\cite{Review2} (Figure~\ref{fig:EfficiencyandFidelity}). 
    The concept of fidelity has garnered significant attention in recent
    years and continues to be an important focus in Digital Twin research~\cite{Review2,Review1}.

    \textbf{Efficiency} refers to the quality of being efficient~\cite{OxfordDictionary}. 
    Therefore, \textit{efficiency} is achieving maximum productivity with minimum wasted resources (Figure~\ref{fig:EfficiencyandFidelity}). 
    It is worth mentioning that the concept of \textit{efficiency} is tightly coupled with the notion of productivity, 
    although \textit{efficiency} differs from the latter's definition, which is defined as the capability to produce large amounts of goods~\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum waste during the process is desired (Figure~\ref{fig:EfficiencyandFidelity}).

    \begin{figure}[htbp]
        \centering
        \includegraphics[width = 1\textwidth]{Efficiency and Fidelity.png}
        \caption{Fidelity (a) and efficiency (b) levels have been demonstrated with simplified CAD drawings and 
        finite state machines.}~\label{fig:EfficiencyandFidelity}
    \end{figure}

    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from \textit{evolvability} in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is an evolvable virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features\cite{ZHANGUPDATEMETHOD}. 
    Furthermore, the evolvability of the digital twin was assessed based on the quantity of effort, which is a necessary resource to initiate transformation
    within the system (Figure~\ref{fig:Evolvability}).

    \begin{figure}[htbp]
        \includegraphics[width = 1\textwidth]{Evolvability.png}
        \caption{Evolvability has been demonstrated with simplified finite state machines. 
        Evolving the machines on the left side, needed effort 
        and the evolved finite state machines on the right side can be observed.}~\label{fig:Evolvability}
    \end{figure}

    \subsection{Mapping Digital Twin Attributes to Manual Review Results}
    To evaluate the quality of the artifact, the issues were mapped to digital twin attributes. 
    To begin this process, the findings were collected from the manual review, followed by an inspection of the findings to determine which digital twin qualities were absent. 
    Finally, the findings were mapped to the relevant missing quality attribute(s) and submitted for artifact quality evaluation (Figure~\ref{fig:RequirementSpecifications}).

    \subsection{Artifact Quality Evaluation}
    To evaluate the quality of the digital twin artifacts, the mapped findings were scrutinized and evaluated. 
    The process started by identifying which quality attribute(s) were mapped. 
    Once identified, the missing attribute(s) was incremented by 1 to determine the total quality of missing attributes of the artifact(Figure~\ref{fig:RequirementSpecifications}).

@@

    \subsection{Digital Twin Quality Evaluation}
    To determine the quality of the digital twin, 
    the values obtained from evaluating each artifact's quality were collected and summed. 
    Furthermore, the value of the sum was assigned to the related digital twin quality attribute. 
    As a result, the digital twin quality was demonstrated with quality attribute values (Figure~\ref{fig:DigitalTwinQuality}).

@@

    First, to assess digital twin quality,
    manual reviews for each artifact were conducted (Figure~\ref{fig:QualityInspectonResultsWithArtifacts} ). 
    As a result, a total of twenty-one quality issues were identified,
    listed, and finally mapped to the digital twin quality attributes(Table~\ref{tab:Table1})(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).
    The mapping process 
    revealed that a total of thirty-eight digital twin quality attributes were 
    lacking in the artifacts(Figure~\ref{fig:QualityInspectonResultsWithArtifacts}).  
    Specifically, 23\% of the quality issues of the digital twin were related to correctness, 
    which indicates an error between the real- and digital twin system. Furthermore, 36\%  were related 
    to completeness, proving that some necessary or appropriate parts were missing.
    Moreover, 8\%  were related to fidelity, indicating a lack of detail. 
    In addition, 5\%  were related to efficiency, indicating poor performance or excessive resource usage.
    And finally, 28\% were related to evolvability, indicating that the system was unresponsive 
    to the environment and was not flexible or scalable.

    \subsection{Example Findings}  
    Two examples(Finding 12, Finding 18) are given to the reader to illustrate 
    the results of the manual review as well as the mapping to the digital twin quality attributes.

    \subsubsection{Conceptual Model-Finding 12:}

@@

    \subsubsection{Simulation Model-Finding 18:}
        The discrete event simulation model enforced a strictly sequential execution of micro-operations,
        which precludes the support of parallel execution. 
        However, machine-human collaboration on a task, needs a parallel execution, especially when the cobot overtakes certain micro-operations. 
        Thus, the exclusion of parallel executions indicates that the simulation model was incomplete,
        at the same time, using the wrong type of execution highlights its inaccuracies(Table~\ref{tab:Table1}) .

@@

    \caption{Mapping of digital twin attributes to the results of the 
    manual reviews: Cases where an attribute is mapped, were marked by `X'.}\label{tab:Table1}

@@

    This paper aimed to evaluate the quality issues with the given digital twin system in the FELICE project while enhancing the 
    scientific understanding of the quality of digital twins. As a result, this study demonstrates the idea of doing a manual review and mapping 
    quality attributes to issues as a suitable approach for evaluating the quality of digital twins in the design phase. Furthermore, 
    the study suggests that this evaluation is an effective way to collect information about the strengths and weaknesses of the digital twin system.
    Although the findings should be interpreted with caution, collected information can be used to improve the upcoming design decisions, consequently to higher-quality digital twin systems.

    However, manual reviews are a time-consuming endeavor, and even with a reasonable investment of resources, it is not feasible that all relevant data will be covered. 
    Additionally, the completeness of manual reviews is questionable due to the inherent limitations of the process. 
    Moreover, the reliance on human judgment in manual reviews presents an additional challenge, as it is subject to individual interpretation and bias.  
    For example, during the walkthrough, the author's assessment of the system could be flawed due to limited information about the designed digital twin system, resulting in false 
    issue identification and mapping. Additionally, those explaining the system to the authors may be biased, 
    whether due to political or economic reasons or lacking explanation ability. As a result, the data gathered from the walkthroughs is highly subjective and lacks objectivity. Lastly, this issue not only shows the severity of the data but also raises concerns about 
    the overall quality of the review process.

    Taken together, the quality assessment of the digital twin encountered limitations due to the exility of information about the real system. 
    Some artifacts provided less information, such as process videos, which gave a limited perspective of the shop floor based on the camera's 
    field of view and the skills of the video maker. In contrast, the simulation and conceptual model offer a plethora of aspects to examine and assess, 
    which results in a higher probability of discovering the issues (Figure~\ref{fig:QualityInspectonResultsWithArtifacts}). 
    A possible explanation for this is the stage that the FELICE project is in. Not only the exility but also the visibility of the information is the limiting factor. 
    Therefore, evolvability, completeness, and correctness were easier to map and detect, rather than fidelity and efficiency.

    It would be interesting to map the risks of the issues instead of the issues to the quality attributes. 
    The risk mapping approach includes severity and priority variables, which would include the perspective of the stakeholders~\cite{CemKanerSoftwareTesting, ISO/IEC/IEEE29119}.
    As a result, quality attributes can be weighted regarding the stakeholder needs.  This aspect might be important because of relativity, 
    more specifically the political and economical nature of the quality~\cite{SystemQuality}.
